---
title: "main"
output: pdf_document
date: "2024-06-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Importing dataset and libraries
```{r df_import, include=FALSE}

df= read.table('/Users/alessandroausteri/Desktop/dab_project/BigMartSales.csv',header=TRUE, sep=",")
library(dplyr)
library(corrplot)
```


Firstly, we are going to fix all features in our dataset, we will start from the feature "Item_Fat_Content".

We can see that there are different names for the same value:

```{r unique values}
item_fat_content_uniques <- unique(df$Item_Fat_Content)#unique values of item_fat_content

print(item_fat_content_uniques)
```
As we can see, we have 2 different names for "Regular Fat" that are "Regular" and "reg"
and 3 different names for "Low Fat" that are "Low fat", "low fat", "LF"

To solve this problem, we can edit the column "Item_Fat_Content" in this way:

all records that start with R or r, will be renamed "Regular Fat", and other will be renamed "Low Fat".

Then we will print the uniques name of the column after the edit

```{r sistemare nomi item_fat_content}
df$Item_Fat_Content <- ifelse(grepl("^[Rr]", df$Item_Fat_Content), "Regular Fat", "Low Fat")
item_fat_content_uniques <- unique(df$Item_Fat_Content)

print(item_fat_content_uniques)

```

Now we should work on the column "Outlet_Size" since analyzing the dataset manually it's clear that there are many missing values.
First of all, we should compute the percentage of missing values.

```{r Outlet size analisy}
#conteggio records senza Outlet_Size:
null<-sum(nchar(df$Outlet_Size) ==0)

#numero di records
total<- nrow(df)

print(paste("Number of rows with missing valuess on Outlet_Size:",null))

#percentuale di righe senza outlet_size
percentuale_stringhe_vuote <- (null / total) * 100

#stampa percentuale di righe senza outlet_size

print(paste("Percentuale di records con stringhe vuote in 'Outlet_Size':", percentuale_stringhe_vuote, "%"))
```

We want to find out if there are relations between the column "Outlet_Type" and the column "Outlet_Size" creating a table to see the number of combination between the outlet size and the outlet type.

```{r outlet_size and outlet_type}
# Creazione di una tabella di riepilogo
outlet_summary <- df %>%
  filter(Outlet_Size %in% c("Small", "Medium", "High")) %>%  # Filtra per includere solo le righe con i valori specificati
  group_by(Outlet_Type, Outlet_Size) %>%  # Raggruppa per tipo e dimensione del negozio
  summarise(Count = n(), .groups = 'drop')  # Calcola il conteggio e rimuove il raggruppamento automatico

# Visualizzazione della tabella di riepilogo
print(outlet_summary)
```
From this tab, we can see that all entries that are "Grocery Store" are small, and all entries that are "Supermarket Type2" or "Supermarket Type3" are Medium.
Knowing this, we can substitute blank values of "Outlet_Size" of grocery with small, of type2 and type 3 with medium.

```{r updating outlet_size}
# Aggiornamento della colonna 'Outlet_Size'
df <- df %>%
  mutate(Outlet_Size = case_when(
    Outlet_Type == "Grocery Store" ~ "Small",
    Outlet_Type %in% c("Supermarket Type2", "Supermarket Type3") ~ "Medium",
    TRUE ~ Outlet_Size  # Mantiene il valore originale per tutte le altre condizioni
  ))

# Visualizza le modifiche per confermare
# Creazione di una tabella di riepilogo
outlet_summary <- df %>%
  filter(Outlet_Size %in% c("Small", "Medium", "High")) %>%  # Filtra per includere solo le righe con i valori specificati
  group_by(Outlet_Type, Outlet_Size) %>%  # Raggruppa per tipo e dimensione del negozio
  summarise(Count = n(), .groups = 'drop')  # Calcola il conteggio e rimuove il raggruppamento automatico

# Visualizzazione della tabella di riepilogo
print(outlet_summary)

```

```{r Outlet size analisy 2}
#conteggio records senza Outlet_Size:
null<-sum(nchar(df$Outlet_Size) ==0)

#numero di records
total<- nrow(df)

print(paste("Number of rows with missing valuess on Outlet_Size:",null))

#percentuale di righe senza outlet_size
percentuale_stringhe_vuote <- (null / total) * 100

#stampa percentuale di righe senza outlet_size

print(paste("Percentuale di records con stringhe vuote in 'Outlet_Size':", percentuale_stringhe_vuote, "%"))
```
Dopo aver riempito grocery store, supermarket type2 e supermarket type3, il numero di na è sceso dal 28% al 21%, passando da 2410 valori mancanti a 1855.

Now we will fill the remaining missing values with n/a
```{r adding na values}
# Aggiornamento della colonna 'Outlet_Size' per riempire le stringhe vuote
df <- df %>%
  mutate(Outlet_Size = if_else(nchar(Outlet_Size) == 0, "NA", Outlet_Size))
```


Now, we want to convert as factor the columns "Item_Fat_Content" giving 0 to "Low Fat" and 1 to "Regular".
And we also want to convert the column Outlet_Size:
  1->Small
  2->Medium
  3->Large

```{r factor converting}

# Conversione di 'Outlet_Size' in valori numerici
df <- df %>%
  mutate(Outlet_Size = case_when(
    Outlet_Size == "Small" ~ 1,
    Outlet_Size == "Medium" ~ 2,
    Outlet_Size == "Large" ~ 3,
    TRUE ~ NA_real_  # Imposta NA per qualsiasi altro valore non specificato
  ))

df <- df%>%
  mutate(Item_Fat_Content = case_when(
    Item_Fat_Content == "Low Fat" ~ 1,
    Item_Fat_Content == "Regular Fat" ~ 2,
    TRUE ~ NA_real_
  ))
head(df)
```
```{r count 0 values}
# Find the number of zero 'Item_Visibility' values for each 'Outlet_Identifier'
zero_visibility_counts <- aggregate(Item_Visibility ~ Outlet_Identifier, data = df, function(x) sum(x == 0))

# Rename the column for better understanding
names(zero_visibility_counts)[2] <- "Zero_Item_Visibility_Count"

# Display the result
print(zero_visibility_counts)
```

```{r count 0 values for each store}

visibility_sum_per_store <- aggregate(Item_Visibility ~ Outlet_Identifier, data = df, sum)
names(visibility_sum_per_store)[2] <- "Total_Item_Visibility"

# Display the result
print(visibility_sum_per_store)
```

```{r total item visibility}
total_visibility_per_store <- aggregate(Item_Visibility ~ Outlet_Identifier, data = df[df$Item_Visibility != 0,], sum)
names(total_visibility_per_store)[2] <- "Total_Item_Visibility"
```

```{r total item visibility 2}
remaining_visibility_per_store <- 100 - total_visibility_per_store$Total_Item_Visibility
remaining_visibility_per_store <- data.frame(Outlet_Identifier = total_visibility_per_store$Outlet_Identifier, Remaining_Visibility = remaining_visibility_per_store)
```

```{r total item visibility 3}
zero_visibility_counts <- aggregate(Item_Visibility ~ Outlet_Identifier, data = df, function(x) sum(x == 0))
names(zero_visibility_counts)[2] <- "Zero_Item_Visibility_Count"
```

```{r total item visibility 4}
df <- merge(df, zero_visibility_counts, by = "Outlet_Identifier", all.x = TRUE)
df <- merge(df, remaining_visibility_per_store, by = "Outlet_Identifier", all.x = TRUE)
```

```{r total item visibility 5}
impute_visibility <- function(item_visibility, zero_count, remaining_visibility) {
  if (item_visibility == 0) {
    if (is.na(zero_count) || zero_count == 0) {
      return(0)  # No zeros to replace, retain zero
    }
    # Check for negative remaining visibility and set to a small positive number if necessary
    if (remaining_visibility < 0) {
      remaining_visibility <- mean(df$Item_Visibility[df$Item_Visibility != 0], na.rm = TRUE)
    }
    return(remaining_visibility / zero_count)
  } else {
    return(item_visibility)
  }
}

# Apply the function to impute zero values
df$Item_Visibility <- mapply(impute_visibility, 
                             df$Item_Visibility, 
                             df$Zero_Item_Visibility_Count, 
                             df$Remaining_Visibility)

```

```{r total item visibility 6}
# Calculate the sum of Item_Visibility for each Outlet_Identifier to verify
visibility_sum_per_store <- aggregate(Item_Visibility ~ Outlet_Identifier, data = df, sum)
names(visibility_sum_per_store)[2] <- "Total_Item_Visibility"

# Display the result
print(visibility_sum_per_store)
```




