---
title: "main"
output: pdf_document
date: "2024-06-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Importing dataset and libraries
```{r setup dell'ambiente}

df= read.table('/Users/alessandroausteri/Desktop/dab_project/BigMartSales.csv',header=TRUE, sep=",")

library(corrplot)
```


Firstly, we are going to fix all features in our dataset, we will start from the feature "Item_Fat_Content".

We can see that there are different names for the same value:

```{r unique values}
item_fat_content_uniques <- unique(df$Item_Fat_Content)#unique values of item_fat_content

print(item_fat_content_uniques)
```
As we can see, we have 2 different names for "Regular Fat" that are "Regular" and "reg"
and 3 different names for "Low Fat" that are "Low fat", "low fat", "LF"

To solve this problem, we can edit the column "Item_Fat_Content" in this way:

all records that start with R or r, will be renamed "Regular Fat", and other will be renamed "Low Fat".

Then we will print the uniques name of the column after the edit

```{r sistemare nomi item_fat_content}
df$Item_Fat_Content <- ifelse(grepl("^[Rr]", df$Item_Fat_Content), "Regular Fat", "Low Fat")
item_fat_content_uniques <- unique(df$Item_Fat_Content)

print(item_fat_content_uniques)

```

